Federated Imputation

### 2020-07-02 federated_imp_synthesizing_complete_data.Rmd
Partitioned data, functions file and some clean-up

The variance of the statistic of interest equals $\bar{v}_M$, which represents the average variance over the $M$ synthetic datasets, when the goal of the synthesis is to make inferences with regard to the sample at hand, instead of with regard to the population. When the goal of the synthesis is to make population inferences, the variance is adjusted with an additional term, based on the number of synthetic datasets: 
$$
Var(Q) = \bar{\mathcal{v}}_M (1 + \frac{1}{M})
$$
where $Q$ is the regression coefficient of the $k^{th}$ variable, $\bar{v}_M$ is the mean of the variables over the $M$ syntheses. If the number of synthesized data points ($J$) is unequal to the number of observations in the dataset ($N$), a correction equal to $\frac{J}{N}$ is multiplied with $\bar{v}_M$.

>>>>

The variance of the statistic of interest equals $\bar{v}_M$, which represents the average variance over the $M$ synthetic datasets, when the goal of the synthesis is to make inferences with regard to the sample at hand, instead of with regard to the population. When the goal of the synthesis is to make population inferences, the variance is adjusted with an additional term, based on the number of synthetic datasets: 
$$
Var(Q) = \bar{\mathcal{v}}_M (1 + \frac{1}{M})
$$
where $Q$ is the statistic of interest and $\bar{v}_M$ is the mean of the statistic over the $M$ syntheses. If the number of synthesized data points ($J$) is unequal to the number of observations in the dataset ($N$), a correction equal to $\frac{J}{N}$ is multiplied with $\bar{v}_M$.
